Scientific Reports Title to see here (20 words or less)

### 2016-06-23 draft1.tex
changed figures to pdfs and updated multiobjective sensitivity

\subsection*{Sensitivity Using Finite Differences}
The derivatives of all parameters were estimated using central differences. 
\begin{equation}
\frac{dh}{d\theta_j} = \frac{h(\theta_0+\frac{e_j}{2})-h(\theta_0-\frac{e_j}{2})}{\delta}
\end{equation}
where $\delta=10^{-8}*\theta_j$ and $e_j$ is a vector of length $\delta$ in the $j^{th}$ direction.
To collapse the time dimension, we calculated overall state sensitivity coefficients. \cite{stelling2004robustness}
\begin{equation}
S_{0j}(t) = \frac{1}{n_s}p_j \left(\sum_{k=1}^{n_t} \sum_{i=1}^{n_s} \left[ \frac{1}{x_i} \frac{dx_i(t_k)}{dp_j} \right]^2 \right)^{1/2}
\end{equation}
where $n_s$ = 1, as $h$ is the only state variable and $n_t$ is the number of time points available for that patient. We calculated sensitivites of parameters that were optimized and not that of those held constant.
\subsubsection*{Single Objective Sensitivity}
From the original values provided by Olufsen and Ottesen, we found that $h_0$ was the most sensitive parameter, followed by $N$, $m_{ach}$, and $m_{nor}$ in that order. Of the four most sensitive equations, three of them ($h_0$, $m_{ach}$ and $m_{nor}$) appear directly in the equation for heart rate, and $N$ indirectly appears, as both $c_{ach}$ and $c_{nor}$ are functions of $N$.
The four parameters that were the most sensitive in our study were among the five most sensitive parameters found by Olufsen and Ottesen, as seen in \ref{tab:OSSCsoriginalParams}.
\subsubsection*{Multiobjective Sensitivity} 
For the multiobjective case, we used the same finite differences, but averaged them not only over the patients, but over the families of parameters-the ten best for each cluster. As with the single objective case, $h_0$ is the most sensitive parameter, followed by $N$, as seen in \ref{fig:MultiobjectiveSensitivityGraph}.
\section*{Discussion}
The Discussion should be succinct and must not contain subheadings.
\section*{Methods}
All calculations were carried out Ubunutu 16.04 using Julia version .0.4.5, with 7.7 GB of available RAM on a Intel Core i7-6700 CPU @ 3.40GHz. Differential equations were solved using the ODE package, with solvers ode23 and ode78, with an absolute and relative tolerance of $10^{-8}$. 
\bibliography{draft1}
\section*{Acknowledgements (not compulsory)}
Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
\section*{Author contributions statement}
Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript. 
\section*{Additional information}
To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement). 
The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

@@

\begin{figure}[ht]
                \centering
        \includegraphics[width=\linewidth]{figures/timedatausingdifferentparamsetsforpatients28611-3018-03-06-18-24n}
       \caption{Performance of the model on a patient in cluster 1. The x represent the true heart rate, the black dots are the mean model prediction from the family of best parameter sets, and the grey gives a 95\% confidence interval.}
       \label{fig:cluster1patientmulti}
\end{figure}
\begin{figure}[ht]
                \centering
        \includegraphics[width=\linewidth]{figures/timedatausingdifferentparamsetsforpatients32582-3106-02-22-22-22n}
       \caption{Performance of the model on a patient in cluster 2. The x represent the true heart rate, the black dots are the mean model prediction from the family of best parameter sets, and the grey gives a 95\% confidence interval.}
       \label{fig:cluster2patientmulti}
\end{figure}
\begin{figure}[ht]
                \centering
       \includegraphics[width=\linewidth]{figures/sumofsilhouettesasafunctionofclustersjustAgeSAPSavgHR}
       \caption{Sum of silhouettes as function of number of clusters}
       \label{fig:sumofsils}
\end{figure}
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/runtimecomparison}
       \caption{Switching from serial to parallel computation resulted in a significant speed up. In parallel operation, six cores were used.}
        \label{fig:executiontime}
\end{figure}
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/MultiobjectiveSenstivityGraph10familiesofNoErrorBars}
       \caption{The black circles are from cluster 1, the grey x's represent cluster 2. Error bars are omitted for the sake of clarity.}
        \label{fig:MultiobjectiveSensitivityGraph}
\end{figure} 
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/TradeOffCurveFasterCooling}
       \caption{The black dots represent the rank 0, or best parameter sets, and the grey dots represent rank 1-4 parameter sets.}
       \label{fig:tradeoffcurve}
\end{figure}
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/TradeOffCurveSlowerCooling}
       \caption{The black dots represent the rank 0, or best parameter sets, and the grey dots represent rank 1-4 parameter sets.}
       \label{fig:tradeoffcurveslower}
\end{figure}

>>>>

\subsection*{Sensitivity Using Finite Differences}
The derivatives of all parameters were estimated using central differences. 
\begin{equation}
\frac{dh}{d\theta_j} = \frac{h(\theta_0+\frac{e_j}{2})-h(\theta_0-\frac{e_j}{2})}{\delta}
\end{equation}
where $\delta=10^{-8}*\theta_j$ and $e_j$ is a vector of length $\delta$ in the $j^{th}$ direction.
To collapse the time dimension, we calculated overall state sensitivity coefficients. \cite{stelling2004robustness}
\begin{equation}
S_{0j}(t) = \frac{1}{n_s}p_j \left(\sum_{k=1}^{n_t} \sum_{i=1}^{n_s} \left[ \frac{1}{x_i} \frac{dx_i(t_k)}{dp_j} \right]^2 \right)^{1/2}
\end{equation}
where $n_s$ = 1, as $h$ is the only state variable and $n_t$ is the number of time points available for that patient. We calculated sensitivites of parameters that were optimized and not that of those held constant.
\subsubsection*{Single Objective Sensitivity}
From the original values provided by Olufsen and Ottesen, we found that $h_0$ was the most sensitive parameter, followed by $N$, $m_{ach}$, and $m_{nor}$ in that order. Of the four most sensitive equations, three of them ($h_0$, $m_{ach}$ and $m_{nor}$) appear directly in the equation for heart rate, and $N$ indirectly appears, as both $c_{ach}$ and $c_{nor}$ are functions of $N$.
The four parameters that were the most sensitive in our study were among the five most sensitive parameters found by Olufsen and Ottesen, as seen in \ref{tab:OSSCsoriginalParams}.
\subsubsection*{Multiobjective Sensitivity} 
For the multiobjective case, we used the same finite differences, but averaged them not only over the patients, but over the families of parameters-the ten best for each cluster. As with the single objective case, $h_0$ is the most sensitive parameter, followed by $N$, as seen in \ref{fig:MultiobjectiveSensitivityGraph} for both clusters, but $N$ is about two times as sensitive in cluster 2 as in cluster one, whereass $h_0$ has nearly the same sensitivity for both clusters. If one were to rank the parameters by sensitivity, the ordering of the four most sensitive parameters between the two clusters is idenitical, however, $\tau_{nor}$ in cluster 2 is approximately an order of magnitude less sensitive than in cluster 1 and $\tau_{ach}$ is nearly three orders of magnitude less senstivie in cluster 2 compared to cluster 1.

If we were to compare to the parameters estimated by Nelder Mead, we find similar sensitivites in $h_0$ and $N$ as well as in $m_{ach}$ and $m_{nor}$. The sensitivities in all of the $\tau$s included in the model is much smaller in the multiobjective case than in the single objective case. Part of this difference in sensitivity may arise from the differences in value found for these parameters by the different methods of optimization.
\section*{Discussion}
The Discussion should be succinct and must not contain subheadings.
\section*{Methods}
All calculations were carried out Ubunutu 16.04 using Julia version .0.4.5, with 7.7 GB of available RAM on a Intel Core i7-6700 CPU @ 3.40GHz. Differential equations were solved using the ODE package, with solvers ode23 and ode78, with an absolute and relative tolerance of $10^{-8}$. 
\bibliography{draft1}
\section*{Acknowledgements (not compulsory)}
Acknowledgements should be brief, and should not include thanks to anonymous referees and editors, or effusive comments. Grant or contribution numbers may be acknowledged.
\section*{Author contributions statement}
Must include all authors, identified by initials, for example:
A.A. conceived the experiment(s),  A.A. and B.A. conducted the experiment(s), C.A. and D.A. analysed the results.  All authors reviewed the manuscript. 
\section*{Additional information}
To include, in this order: \textbf{Accession codes} (where applicable); \textbf{Competing financial interests} (mandatory statement). 
The corresponding author is responsible for submitting a \href{http://www.nature.com/srep/policies/index.html#competing}{competing financial interests statement} on behalf of all authors of the paper. This statement must be included in the submitted article file.

@@

\begin{figure}[ht]
                \centering
        \includegraphics[width=\linewidth]{figures/timedatausingdifferentparamsetsforpatients28611-3018-03-06-18-24n}
       \caption{Performance of the model on a patient in cluster 1. The x represent the true heart rate, the black dots are the mean model prediction from the family of best parameter sets, and the grey gives a 95\% confidence interval.}
       \label{fig:cluster1patientmulti}
\end{figure}
\begin{figure}[ht]
                \centering
        \includegraphics[width=\linewidth]{figures/timedatausingdifferentparamsetsforpatients32582-3106-02-22-22-22n}
       \caption{Performance of the model on a patient in cluster 2. The x represent the true heart rate, the black dots are the mean model prediction from the family of best parameter sets, and the grey gives a 95\% confidence interval.}
       \label{fig:cluster2patientmulti}
\end{figure}
\begin{figure}[ht]
                \centering
       \includegraphics[width=\linewidth]{figures/sumofsilhouettesasafunctionofclustersjustAgeSAPSavgHR}
       \caption{Sum of silhouettes as function of number of clusters}
       \label{fig:sumofsils}
\end{figure}
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/runtimecomparison}
       \caption{Switching from serial to parallel computation resulted in a significant speed up. In parallel operation, six cores were used.}
        \label{fig:executiontime}
\end{figure}
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/MultiobjectiveSenstivityGraph10familiesofNoErrorBarsJun22}
       \caption{The black circles are from cluster 1, the grey x's represent cluster 2. Error bars are omitted for the sake of clarity.}
        \label{fig:MultiobjectiveSensitivityGraph}
\end{figure} 
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/TradeOffCurveFasterCooling}
       \caption{The black dots represent the rank 0, or best parameter sets, and the grey dots represent rank 1-4 parameter sets.}
       \label{fig:tradeoffcurve}
\end{figure}
\begin{figure}[ht]
       \centering
       \includegraphics[width=\linewidth]{figures/TradeOffCurveSlowerCooling}
       \caption{The black dots represent the rank 0, or best parameter sets, and the grey dots represent rank 1-4 parameter sets.}
       \label{fig:tradeoffcurveslower}
\end{figure}
